\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{enumitem}
\setlist[enumerate,1]{label=\arabic*.}
\setlist[enumerate,2]{label=\arabic*)}

\begin{document}

\title{GATE 2022 \\ General Aptitude \& Geomatics Engineering}
\author{}
\date{}
\maketitle

\begin{enumerate}

\item Writing too many things on the \_\_\_\_\_\_ while teaching could make the students get \_\_\_\_\_.
\begin{enumerate}
    \item bored / board
    \item board / bored
    \item board / board
    \item bored / bored
\end{enumerate}

\item Which one of the following is a representation (not to scale and in bold) of all values of $x$ satisfying the inequality $2 - 5x \le -$ on the real number line? [Diagram omitted]
\begin{enumerate}
    \item Option 1
    \item Option 2
    \item Option 3
    \item Option 4
\end{enumerate}

\item If $f(x) = 2 \ln \sqrt{e}$, what is the area bounded by $f(x)$ for the interval $[0, 2]$ on the $x$-axis?
\begin{enumerate}
    \item $\frac{1}{2}$
    \item $1$
    \item $2$
    \item $4$
\end{enumerate}

\item A person was born on the fifth Monday of February in a particular year. Which one of the following statements is correct?
\begin{enumerate}
    \item The 2nd February of that year is a Tuesday
    \item There will be five Sundays in February in that year
    \item The 1st February of that year is a Sunday
    \item All Mondays of February in that year have even dates
\end{enumerate}

\item Which one of the groups given below can be assembled to get the shape shown above without overlapping? [Diagram omitted]
\begin{enumerate}
    \item Option 1
    \item Option 2
    \item Option 3
    \item Option 4
\end{enumerate}

\item Fish belonging to species S in the deep sea have ultra-black skin... Which one of the following is the CORRECT logical inference?
\begin{enumerate}
    \item Having ultra-black skin is only advantageous to species S
    \item Species S with lower collagen in their skin are at an advantage because it helps them avoid predators
    \item Having ultra-black skin has both advantages and disadvantages to species S
    \item Having ultra-black skin is only disadvantageous to species S but advantageous only to their predators
\end{enumerate}

\item For the past $m$ days, the average daily production was 100 units/day. If today’s production of 180 units changes the average to 110 units/day, what is the value of $m$?
\begin{enumerate}
    \item 18
    \item 10
    \item 7
    \item 5
\end{enumerate}

\item Consider the following functions for non-zero positive integers $p$ and $q$. [Equations omitted] Which one of the following options is correct?
\begin{enumerate}
    \item $f(2,2) = g(2,2)$
    \item $f(g(2,2), 2) < f(2, g(2,2))$
    \item $g(2,1) \ne f(2,1)$
    \item $f(3,2) > g(3,2)$
\end{enumerate}

\item Four cities P, Q, R, S are connected through one-way routes. [Diagram omitted] If the person starts from R at 7 AM, visits S and returns to R, what is the minimum time required?
\begin{enumerate}
    \item 6 hours 30 minutes
    \item 3 hours 45 minutes
    \item 4 hours 30 minutes
    \item 5 hours 15 minutes
\end{enumerate}

\item Equal sized circular regions are shaded in a square sheet of side 1 cm. Case M and N as shown. What is the ratio of the unshaded regions (M:N)? [Diagram omitted]
\begin{enumerate}
    \item 2:3
    \item 1:1
    \item 3:2
    \item 2:1
\end{enumerate}

\item Most probable value of a quantity:
\begin{enumerate}
    \item always increases with increase in True value
    \item always decreases with decrease in True value
    \item is always equal to True value
    \item is nearest to True value
\end{enumerate}

\item Two surveyors P and Q measured a 20 m distance six times each. Based on accuracy and precision, choose the correct statement:
\begin{enumerate}
    \item P less precise, Q more accurate
    \item P more precise, Q less accurate
    \item P more accurate, Q more precise
    \item P less accurate, Q less precise
\end{enumerate}

\item Identify the error:
\begin{enumerate}
    \item Mistake
    \item Cumulative error
    \item Probable error
    \item Accidental error
\end{enumerate}

\item Electromagnetic Spectrum (in increasing wavelength):
\begin{enumerate}
    \item X-rays, Gamma, Infrared, Ultraviolet, Visible, Radiowave, Microwave
    \item Gamma, X-rays, Radiowave, Microwave, Ultraviolet, Infrared, Visible
    \item X-rays, Gamma, Microwave, Radiowave, Ultraviolet, Infrared, Visible
    \item Gamma, X-rays, Ultraviolet, Visible, Infrared, Microwave, Radiowave
\end{enumerate}

\item Relationship between wavelength $\lambda$, frequency $\nu$, and velocity $c$:
\begin{enumerate}
    \item $c = \nu^2 / \lambda$
    \item $c = \nu / \lambda$
    \item $c = \nu \lambda$
    \item $c = \nu \lambda^2$
\end{enumerate}

\item Spectral signature of an object in a satellite image does NOT depend on:
\begin{enumerate}
    \item season of the year
    \item wavelength of EM spectrum
    \item swath width of the satellite
    \item reflectance value from the object
\end{enumerate}

\item Component of GPS signal deciphered by all types of GPS receivers:
\begin{enumerate}
    \item Coarse-Acquisition code
    \item Precision code
    \item Link-1 frequency
    \item Link-2C frequency
\end{enumerate}

\item For 3D-positioning, GNSS requires a minimum of \_\_\_ satellites.
\begin{enumerate}
    \item 3
    \item 4
    \item 5
    \item 2
\end{enumerate}

\item Basic objective of NAVSTAR GPS:
\begin{enumerate}
    \item Positioning, Velocity and Timing
    \item Positioning, Navigation and Timing
    \item Velocity, Navigation and Timing
    \item Positioning, Velocity and Navigation
\end{enumerate}

\item A satellite image with 6-bit radiometric resolution has \_\_\_ gray levels.
\begin{enumerate}
    \item 16
    \item 32
    \item 64
    \item 128
\end{enumerate}

\end{enumerate}

\end{document}
